---
title: "Replication of 'Sick Body, Vigilant Mind'"
author: "Josh Tybur, Ben Jones, Lisa DeBruine"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
  html_notebook:
    code_folding: show
    toc: yes
---

```{r libraries, message=FALSE}
library(TOSTER) # for equivalence tests
library(afex) # for SPSS-style ANOVAs; also loads lme4 and lmerTest for LMEMs
library(tidyverse) # for data wrangling
```

## Load and Process Data from Inquisit

```{r load-data}
dat.raw <- read_tsv("../Dot_Probe_raw.dat")
```

```{r get-trials}
trials <- dat.raw %>%
  mutate(
    stim_id = str_replace(stimulusitem3, ".bmp", ""),
    target = str_replace(stimulusitem5, ".bmp", "")
  ) %>%
  select(-(stimulusitem1:stimulusitem5)) %>%
  filter(blockcode != "practice") %>%
  separate(trialcode, c("real", "position", "trial_type", "block")) %>%
  separate(stim_id, c("w", "face_sex", "face_type", "face_n"), sep = c(1, 2,3), remove = F) %>%
  select(-real, -w, -face_n) %>%
  mutate( # circle = 18, square = 23
    correct = case_when(
      target == "circle" & response == 18 ~ 1,
      target == "square" & response == 23 ~ 1,
      TRUE ~ 0
    ),
    face_type = recode(face_type, "d" = "disfigured", "n" = "normal")
  ) %>%
  rename(rt = latency, user_id = subject)
```


### Simulate Raters

* recency (4 items) Illness recency
* PVDpi (7 items) Perceived infectability subscale of PVD
* PVDga (7 items) Germ aversion subscale of PVD
* pd (7 items) Pathogen disgust subscale of TDDS
* img (7 items) Pathogen images from Curtis

```{r sim-raters}

n <- 300 #original = 96

raters <- tibble(
  user_id = 1:n,
  sex = c(rep("male", ceiling(36/96*n)), 
          rep("female", floor(60/96*n))
          ),
  age = sample(18:30, n, replace = T),
  # distrubute so ~28% are recently ill
  recent_cold = sample(1:7, n, replace = T, 
                       prob = c(.05, .10, .13, .44, .13, .10, .05)),
  recency_1 = sample(1:7, n, replace = T),
  recency_2 = sample(1:7, n, replace = T),
  recency_3 = sample(1:7, n, replace = T),
  recency_4 = sample(1:7, n, replace = T),
  PVDpi_1 = sample(0:6, n, replace = T),
  PVDpi_2 = sample(0:6, n, replace = T),
  PVDpi_3 = sample(0:6, n, replace = T),
  PVDpi_4 = sample(0:6, n, replace = T),
  PVDpi_5 = sample(0:6, n, replace = T),
  PVDpi_6 = sample(0:6, n, replace = T),
  PVDpi_7 = sample(0:6, n, replace = T),
  PVDga_1 = sample(0:6, n, replace = T),
  PVDga_2 = sample(0:6, n, replace = T),
  PVDga_3 = sample(0:6, n, replace = T),
  PVDga_4 = sample(0:6, n, replace = T),
  PVDga_5 = sample(0:6, n, replace = T),
  PVDga_6 = sample(0:6, n, replace = T),
  PVDga_7 = sample(0:6, n, replace = T),
  PVDga_8 = sample(0:6, n, replace = T),
  pd_1 = sample(0:6, n, replace = T),
  pd_2 = sample(0:6, n, replace = T),
  pd_3 = sample(0:6, n, replace = T),
  pd_4 = sample(0:6, n, replace = T),
  pd_5 = sample(0:6, n, replace = T),
  pd_6 = sample(0:6, n, replace = T),
  pd_7 = sample(0:6, n, replace = T),
  img_1 = sample(1:7, n, replace = T),
  img_2 = sample(1:7, n, replace = T),
  img_3 = sample(1:7, n, replace = T),
  img_4 = sample(1:7, n, replace = T),
  img_5 = sample(1:7, n, replace = T),
  img_6 = sample(1:7, n, replace = T),
  img_7 = sample(1:7, n, replace = T),
  img_8 = sample(1:7, n, replace = T)
) 

```

### Recode

```{r recode-raters}

raters_coded <- raters %>%
  mutate(
    recent_cold = case_when(
      recent_cold %in% 1:3 ~ "recent",
      recent_cold %in% 4:7 ~ "not recent"
    )
  ) %>%
  gather(var, score, recency_1:img_8) %>%
  separate(var, c("var", "var_n")) %>%
  group_by(user_id, sex, age, recent_cold, var) %>%
  summarise(score = mean(score)) %>%
  ungroup() %>%
  spread(var, score)
  
```

### Simulate Trials

```{r sim-trials}
trials <- expand.grid(
  user_id = 1:n,
  trial = 1:80
) %>%
  mutate(
    trial_type = ifelse(trial <= 80*.4, "same", "diff"),
    face_type = as.factor(ifelse(trial%%2 == 0, "disfigured", "normal")),
    correct = sample(0:1, nrow(.), replace = T, prob = c(.1, .9)),
    rt = rnorm(nrow(.), 620, 160) # approx mean & sd from SBVM
  )
```

### Exclusions

"Trials with incorrect categorization responses and trials with latencies greater than 3 standard deviations above or below a participant's mean latency were excluded. Two participants had high error rates (> 3 SD above the mean) and were excluded." (Miller & Maner)

```{r exclusions}

trials_inc <- trials %>%
  filter(correct == 1, trial_type == "diff") %>%
  group_by(user_id) %>%
  mutate(mean_rt = mean(rt),
         sd_rt = sd(rt),
         n_correct = n()) %>%
  filter(rt <= mean_rt + 3*sd_rt, rt >= mean_rt - 3*sd_rt) %>%
  ungroup() %>%
  group_by() %>%
  filter(n_correct >= mean(n_correct) - 3*sd(n_correct)) %>%
  ungroup()
  
```

### Join Data

```{r join-data}

# centre and scale continuous scores from only included raters
raters_inc <- raters_coded %>%
  semi_join(trials_inc, by = "user_id") %>%
  mutate(
    recent_cold = as.factor(recent_cold),
    recency.z = (recency - mean(recency)) / sd(recency),
    PVDga.z = (PVDga - mean(PVDga)) / sd(PVDga),
    PVDpi.z = (PVDpi - mean(PVDpi)) / sd(PVDpi)
  )

data_agg <- trials_inc %>%
  group_by(user_id, face_type) %>%
  summarise(rt = mean(rt)) %>%
  ungroup() %>%
  left_join(raters_inc, by = "user_id")

```


## Descriptives

### Demographics
```{r demog}
raters_coded %>%
  group_by(sex) %>%
  summarise(
    n = n(),
    mean_age = mean(age, na.rm = T),
    sd_age = sd(age, na.rm = T)
  ) %>%
  bind_rows(raters_coded %>%
    group_by() %>%
    summarise(
      n = n(),
      mean_age = mean(age, na.rm = T),
      sd_age = sd(age, na.rm = T)
    ) %>%
    mutate(sex = "TOTAL")
  ) %>%
  mutate_if(is.numeric, round, 2)
```

### Included trials

```{r included-trials}
trials_inc %>%
  group_by(user_id, face_type) %>%
  summarise(included_trials = n()) %>%
  group_by(face_type) %>%
  summarise(n = n(),
            mean = mean(included_trials),
            min = min(included_trials),
            max = max(included_trials)
  ) %>%
  mutate_if(is.numeric, round, 2)
  
```

### RTs by trial

```{r trial-rt-plot}
trials_inc %>%
  ggplot(aes(rt, color = face_type, group = as.factor(trial))) +
  geom_density() +
  scale_color_manual(values = c("#CC0000", "#006699"), name = "Face Type") +
  theme_minimal()
```

### Illness Variables

```{r illness-plot}
raters_coded %>%
  gather(variable, score, recency, PVDga, PVDpi) %>%
  ggplot(aes(score, color = variable)) +
  geom_density()
```


### Face Type by Recent Cold
```{r facetype-recency-table}
data_agg %>%
  group_by(face_type, recent_cold) %>%
  summarise(n = n(),
            mean = mean(rt),
            sd = sd(rt)
  ) %>%
  mutate_if(is.numeric, round, 3)
```

```{r facetype-recency-plot}
ggplot(data_agg, aes(recent_cold, rt, color = face_type)) +
  geom_violin(aes(fill = face_type), alpha = 0.25) +
  geom_boxplot(width = 0.2, outlier.size = 0,
               position = position_dodge(width = 0.9),
               show.legend = F) +
  labs(x = "Recency of Cold",
       y = "Mean RT on Attentional Shift Trials") +
  scale_color_manual(values = c("#CC0000", "#006699"), name = "Face Type") +
  scale_fill_manual(values = c("#CC0000", "#006699"), guide = F) +
  theme_minimal()
```


## Analyses

### Reaction Time DV

#### Analysis 1A: Categorical illness recency
```{r analysis-1a}

cat_ANOVA <- aov_4(rt ~ recent_cold * face_type + 
                     (1 + face_type | user_id), 
              data = data_agg, factorize = FALSE)

anova(cat_ANOVA, es = "pes", MSE = FALSE)

```

#### Analysis 1B: Recent illness
```{r analysis-1b}

recent_ill <- filter(data_agg, recent_cold == "recent")
t.test(recent_ill$rt~recent_ill$face_type)

```

#### Analysis 1C: Non-Recent illness
```{r analysis-1c}

not_recent_ill <- filter(data_agg, recent_cold == "not recent")
t.test(not_recent_ill$rt~not_recent_ill$face_type)

```

#### Analysis 1D: Equivalence Tests

```{r}
stats_cat <- data_agg %>%
  spread(face_type, rt, convert = T) %>%
  mutate(dv = disfigured - normal) %>%
  group_by(recent_cold) %>%
  summarise(n = n(),
            m = mean(dv),
            sd = sd(dv)
  )

n1 <- stats_cat %>% filter(recent_cold == "not recent") %>% pull(n)
n2 <- stats_cat %>% filter(recent_cold == "recent") %>% pull(n)
m1 <- stats_cat %>% filter(recent_cold == "not recent") %>% pull(m)
m2 <- stats_cat %>% filter(recent_cold == "recent") %>% pull(m)
sd1 <- stats_cat %>% filter(recent_cold == "not recent") %>% pull(sd)
sd2 <- stats_cat %>% filter(recent_cold == "recent") %>% pull(sd)
low_eqbound_dz <- -.35
high_eqbound_dz <- .35

TOSTtwo(m1, m2, sd1, sd2, n1, n2, low_eqbound_dz, high_eqbound_dz)
```


### Continuous illness recency

```{r analysis-1a-continuous}

cont_ANOVA <- aov_4(rt ~ recency.z * face_type + 
                      (1 + face_type | user_id), 
              data = data_agg, factorize = FALSE)

anova(cont_ANOVA, es = "pes", MSE = FALSE)

```


### Self-report Measures

Difference in PVD between recently ill and non-recently ill groups

#### Analysis 2A: Perceived Infectability
```{r diff-PVDpi}
t.test(data_agg$PVDpi~data_agg$recent_cold)
```

#### Analysis 2B: Germ Aversion
```{r diff-PVDga}
t.test(data_agg$PVDga~data_agg$recent_cold)
```

#### Analysis 2C: TDDS
```{r diff-pd}
t.test(data_agg$pd~data_agg$recent_cold)
```

#### Analysis 2D: Curtis Images
```{r diff-img}
t.test(data_agg$img~data_agg$recent_cold)
```
