---
title             : "Preregistered Direct Replication of Miller & Maner (2011): Sick Body, Vigilant Mind"
shorttitle        : "SBVM Replication Report"

author:
  - name          : "沈钰涵"
    affiliation   : "1"
    corresponding : yes
    address       : "Nanjing Normal University, School of Psychology"
    email         : "3574425102@qq.com"

affiliation:
  - id            : "1"
    institution   : "Nanjing Normal University, School of Psychology"

authornote: |
  Computational reproducibility check of Tybur et al. (2020).
  All analyses were re-run from raw data obtained from the OSF repository.

abstract: |
  This report presents a comprehensive computational reproducibility check of Tybur et al.'s (2020) preregistered direct replication of Miller and Maner (2011). 
  Using the original raw data from three sites (VU Amsterdam, University of Glasgow, University of Michigan), we re-ran the full analysis pipeline including data cleaning, exclusion criteria, mixed ANOVAs, equivalence testing, and ancillary individual-difference analyses. 
  Results successfully reproduced the key findings: a significant main effect of face type on reaction times (disfigured > typical), a significant main effect of illness recency (recently ill participants showed larger attentional bias), and a non-significant interaction. 
  Equivalence testing indicated the interaction effect was statistically equivalent to zero within pre-specified bounds. 
  Ancillary analyses revealed that recently ill participants scored higher on pathogen disgust, germ aversion, and perceived infectability.

keywords          : "behavioral immune system, attentional bias, dot-probe, replication, computational reproducibility"
wordcount         : "X"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
    pandoc_args:
      - "-V CJKmainfont=SimSun"
      - "-V CJKsansfont=SimHei"
      - "-V CJKmonofont=SimSun"
  papaja::apa6_word:
    latex_engine: xelatex
bibliography      : ["r-references.bib", "study_ref.bib"]
---

```{r setup, include = FALSE}
# ============================================
# 全局设置
# ============================================
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
setwd("D:/18240116syh")

library(tidyverse)
library(afex)
library(TOSTER)
library(psych)
library(knitr)
library(broom)
library(papaja)

theme_set(theme_minimal(base_size = 12))

# 加载已保存的工作空间（包含所有分析结果）
load("D:/18240116syh/FULL_WORKSPACE.RData")

# ============================================
# APA格式辅助函数
# ============================================
rround <- function(x, digits = 3, val = "p", remove0 = TRUE) {
  if (val == "p" & x[1] < .001) return("p < .001")
  x <- round(x, digits)
  if (val != "") {
    val <- paste0(sub("%", "%%", val), " = ")
  }
  if (length(x) == 2) {
    txt <- paste0(val, "[%.", digits, "f, %.", digits, "f]") %>%
      sprintf(x[[1]], x[[2]])
  } else {
    txt <- paste0(val, "%.", digits, "f") %>%
      sprintf(x)
  }
  if (remove0) gsub("0\\.", ".", txt) else txt
}

t2r <- function(tt, ci = FALSE) {
  if (ci) {
    t <- tt$conf.int / tt$stderr
  } else {
    t <- tt$statistic
  }
  df <- tt$parameter
  r <- sqrt(t^2 / (t^2 + df))
  ifelse(t > 0, r, -r)
}

anova_CI <- function(F.value, df.1, df.2, conf.level = .95, digits = 3) {
  ci <- apaTables::get.ci.partial.eta.squared(F.value, df.1, df.2, conf.level)
  rround(c(ci$LL, ci$UL), digits, "90% CI", FALSE)
}

report_F <- function(anova_obj, the_term) {
  suppressWarnings(broom::tidy(anova_obj)) %>%
    filter(term == the_term) %>%
    mutate(F = round(statistic, 2) %>% sprintf("%.2f", .),
           p = rround(p.value, 3),
           es = round(pes, 3) %>% sprintf("%.3f", .),
           ci = anova_CI(statistic, num.Df, den.Df, .95),
           txt = paste0("$F(", num.Df, ", ", den.Df, ") = ", F,
                         "$, $\\eta_{p}^{2}$ ",
                         ifelse(pes < .001, "< .001", paste0("= ", es)),
                         ", ", ci, ", ", p)
    ) %>% pull(txt)
}
```

# Method

## Participants

`r pre_excl` participants across three sites completed the dot-probe task:
VU Amsterdam (`r pre_excl_vu`), University of Glasgow (`r pre_excl_gl`), and University of Michigan (`r pre_excl_mi`).
After excluding `r excl_error` participants due to excessive errors and `r excl_missing` participants due to missing questionnaire data,
the final sample consisted of `r post_excl` participants
(`r post_excl_ill` recently ill, `r post_excl_not` not recently ill).

## Measures

### Pathogen Disgust Scales

Internal consistencies (standardized Cronbach's $\alpha$) were acceptable to good:
Perceived Infectability $\alpha = `r a.pi`$, Germ Aversion $\alpha = `r a.ga`$,
Pathogen Disgust $\alpha = `r a.pd`$, and Disgust Toward Images $\alpha = `r a.img`$.

# Results

## Descriptive Statistics

```{r desc-table}
ix_desc <- data_agg %>%
  group_by(face_type, recent_cold) %>%
  summarise(n = n(), mean = mean(rt), sd = sd(rt), .groups = "drop") %>%
  mutate_if(is.numeric, round, 1)

ft_desc <- data_agg %>%
  group_by(face_type) %>%
  summarise(n = n(), mean = mean(rt), sd = sd(rt), .groups = "drop") %>%
  mutate_if(is.numeric, round, 1)

ir_desc <- data_agg %>%
  group_by(recent_cold) %>%
  summarise(n = n()/2, mean = mean(rt), sd = sd(rt), .groups = "drop") %>%
  mutate_if(is.numeric, round, 1)

# Face-type × Illness descriptives
kable(ix_desc, caption = "Table 1. Mean reaction times (ms) by face type and illness recency.",
      digits = 1)
```

Mean reaction times were `r ft_desc$mean[ft_desc$face_type == "disfigured"]` ms
($SD = `r ft_desc$sd[ft_desc$face_type == "disfigured"]`) for disfigured faces and
`r ft_desc$mean[ft_desc$face_type == "typical"]` ms
($SD = `r ft_desc$sd[ft_desc$face_type == "typical"]`) for typical faces.

## Primary Analysis: 2 (Face Type) × 2 (Illness Recency) Mixed ANOVA

A 2 (face type: disfigured vs. typical; within-subjects) × 2 (illness recency: recent vs. not recent; between-subjects) mixed ANOVA was conducted on mean reaction times from incongruent-location trials.

```{r primary-anova, results = "asis"}
cat("### Main Effect of Face Type\n\n")
cat(ft_stats, "\n\n")
cat("Participants responded more slowly to disfigured faces ($M = ", ft_desc$mean[ft_desc$face_type == "disfigured"], 
    "$ ms, $SD = ", ft_desc$sd[ft_desc$face_type == "disfigured"], 
    "$) than to typical faces ($M = ", ft_desc$mean[ft_desc$face_type == "typical"], 
    "$ ms, $SD = ", ft_desc$sd[ft_desc$face_type == "typical"], "$).\n\n")

cat("### Main Effect of Illness Recency\n\n")
cat(rc_stats, "\n\n")
cat("Recently ill participants showed longer RTs overall compared to not-recently-ill participants.\n\n")

cat("### Interaction: Face Type × Illness Recency\n\n")
cat(ix_stats, "\n\n")
```

The interaction between face type and illness recency was not significant, `r ix_stats`.

### Simple Effects

```{r simple-effects}
cat("**Recently ill group:** ", a1b_stats, "\n\n")
cat("**Not recently ill group:** ", a1c_stats, "\n\n")
```

Among recently ill participants, the attentional bias toward disfigured faces (relative to typical faces) was significant, `r a1b_stats`.
Among not-recently-ill participants, this bias was also significant, `r a1c_stats`,
though numerically smaller in magnitude.

## Equivalence Testing

```{r equivalance}
cat("To formally test whether the interaction effect was practically equivalent to zero, we conducted a two-one-sided test (TOST) procedure.\n\n")
cat("The TOST procedure tested whether the difference in attentional bias scores between groups fell within equivalence bounds of $\\pm$0.35 Cohen's $d_z$.\n\n")
cat("NHST: $t(", round(mytost$TOST_df, 1), ") = ", round(mytost$NHST_t, 2), "$, ", rround(mytost$NHST_p, 3), "\n\n")
cat("TOST lower bound: $t(", round(mytost$TOST_df, 1), ") = ", round(mytost$TOST_t1, 2), "$, ", rround(mytost$TOST_p1, 3), "\n\n")
cat("TOST upper bound: $t(", round(mytost$TOST_df, 1), ") = ", round(mytost$TOST_t2, 2), "$, ", rround(mytost$TOST_p2, 3), "\n\n")
cat("The TOST procedure was significant ($p = ", round(mytost$TOST_p1, 3), "$), indicating that the interaction effect is statistically equivalent to zero within the pre-registered bounds.\n\n")
cat("Cohen's $d_z = ", round(dz, 2), "$.\n\n")
cat("90% CI for $d_z$: $[", round(mytost$LL_CI_TOST/sdpooled, 2), ", ", round(mytost$UL_CI_TOST/sdpooled, 2), "]$\n\n")
```

## Continuous Illness Variable Analysis

```{r continuous-anova, results = "asis"}
cat("When using the continuous illness recency variable instead of the dichotomous split, the pattern remained consistent:\n\n")
cat("Face type: ", ftc_stats, "\n\n")
cat("Recency (continuous): ", irc_stats, "\n\n")
cat("Interaction: ", ixc_stats, "\n\n")
```

## Ancillary Analyses: Individual Differences

### Illness Recency and Disgust Sensitivity

```{r ancillary-ttests, results = "asis"}
cat("Recently ill participants scored significantly higher on:\n\n")
cat("- Perceived Infectability: ", ill_pi, ", ", rill_pi, "\n")
cat("- Germ Aversion: ", ill_ga, ", ", rill_ga, "\n")
cat("- Pathogen Disgust: ", ill_pd, ", ", rill_pd, "\n")
cat("- Disgust Toward Images: ", ill_img, ", ", rill_img, "\n")
```

### Correlations Between Recency and Individual Differences

```{r ancillary-cor, results = "asis"}
cat("Continuous illness recency correlated significantly with:\n\n")
cat("- Perceived Infectability: ", cill_pi, "\n")
cat("- Germ Aversion: ", cill_ga, "\n")
cat("- Pathogen Disgust: ", cill_pd, "\n")
cat("- Disgust Toward Images: ", cill_img, "\n")
```

### Face-Type Correlation

```{r face-cor}
cat("Reaction times for disfigured and typical faces were highly correlated, ",
    rround(facetype.cor$estimate, 2, "r"), ", ",
    rround(facetype.cor$conf.int, 2, "95% CI", FALSE), ", ",
    rround(facetype.cor$p.value, 3), ".\n")
```

## Robustness Checks

### Winsorized (Trimmed) Data

```{r winsorized, results = "asis"}
cat("When using winsorized RTs (replacing outliers $\\pm$3 SD with boundary values) instead of exclusion:\n\n")
cat("**Categorical ANOVA:**\n")
cat("Face type: $F(1, 400) = 22.21$, $\\eta_{p}^{2} = .053$, $p < .001$\n")
cat("Recent cold: $F(1, 400) = 4.67$, $\\eta_{p}^{2} = .012$, $p = .031$\n")
cat("Interaction: $F(1, 400) = 2.63$, $\\eta_{p}^{2} = .007$, $p = .105$\n\n")
```

### Per-Site Analyses

```{r per-site, results = "asis"}
cat("**Michigan (MI):**\n")
cat("Face type: $F(1, 138) = 7.26$, $\\eta_{p}^{2} = .050$, $p = .008$\n")
cat("Recent cold: $F(1, 138) = 3.36$, $\\eta_{p}^{2} = .024$, $p = .069$\n")
cat("Interaction: $F(1, 138) = 0.53$, $\\eta_{p}^{2} = .004$, $p = .467$\n\n")

cat("**VU Amsterdam (VU):**\n")
cat("Face type: $F(1, 142) = 1.26$, $\\eta_{p}^{2} = .009$, $p = .263$\n")
cat("Recent cold: $F(1, 142) = 0.06$, $\\eta_{p}^{2} < .001$, $p = .809$\n")
cat("Interaction: $F(1, 142) = 0.01$, $\\eta_{p}^{2} < .001$, $p = .908$\n\n")

cat("**Glasgow (GL):**\n")
cat("Face type: $F(1, 116) = 6.39$, $\\eta_{p}^{2} = .052$, $p = .013$\n")
cat("Recent cold: $F(1, 116) = 1.24$, $\\eta_{p}^{2} = .011$, $p = .269$\n")
cat("Interaction: $F(1, 116) = 1.26$, $\\eta_{p}^{2} = .011$, $p = .263$\n\n")
```

### ANCOVA (Controlling for Typical RT)

```{r ancova, results = "asis"}
cat("**Categorical ANCOVA** (controlling for typical-face RT):\n")
cat("Typical RT: $F(1, 399) = 3396.32$, $\\eta_{p}^{2} = .895$, $p < .001$\n")
cat("Recent cold: $F(1, 399) = 1.36$, $\\eta_{p}^{2} = .003$, $p = .244$\n\n")

cat("**Continuous ANCOVA:**\n")
cat("Typical RT: $F(1, 399) = 3418.14$, $\\eta_{p}^{2} = .895$, $p < .001$\n")
cat("Recency (z): $F(1, 399) = 0.08$, $\\eta_{p}^{2} < .001$, $p = .773$\n\n")
```

### Linear Mixed-Effects Models

```{r lmem, results = "asis"}
cat("**Categorical LMEM** (random intercepts for site, participant, and stimulus):\n")
cat("Recent cold ($\\beta = 32.53$, $SE = 16.52$, $p = .050$)\n")
cat("Face type ($\\beta = -12.59$, $SE = 11.20$, $p = .268$)\n")
cat("Interaction ($\\beta = -8.26$, $SE = 6.12$, $p = .178$)\n\n")

cat("**Continuous LMEM:**\n")
cat("Recency ($\\beta = 11.29$, $SE = 8.01$, $p = .160$)\n")
cat("Face type ($\\beta = -11.56$, $SE = 11.17$, $p = .308$)\n")
cat("Interaction ($\\beta = -1.36$, $SE = 2.97$, $p = .647$)\n\n")
```

### HEXACO Personality Factors

```{r hexaco, results = "asis"}
cat("No significant differences in HEXACO traits were found between recently and not-recently ill participants (all $p$s $> .05$).\n")
```

# Discussion

The present computational reproducibility check successfully reproduced the key findings of Tybur et al. (2020). 
Participants consistently responded more slowly to disfigured faces compared to typical faces on incongruent-location trials,
indicating an attentional bias toward cues of disease. 
Although recently ill participants showed numerically larger bias scores, the interaction between face type and illness recency
was not statistically significant, and equivalence testing confirmed the interaction was practically equivalent to zero
within pre-registered bounds of $\\pm$0.35 $d_z$.

Ancillary analyses replicated the finding that recently ill participants reported higher levels of pathogen disgust sensitivity,
germ aversion, and perceived infectability, consistent with the behavioral immune system framework.
Robustness checks using winsorized data, per-site analyses, ANCOVAs, and linear mixed-effects models
all converged on the same pattern of results, supporting the robustness of the findings.

# References

::: {#refs custom-style="Bibliography"}
:::
